On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-08 manuscripts/IEEE/final_submission.tex
minor

%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
%\title{When is the dictionary learning problem well-posed?}
\title{On the uniqueness and stability of dictionaries for sparse representation of noisy signals}
%\title{When is the dictionary learning problem for sparse coding well-posed?}
%\title{When is the sparsest representation unique?}
%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.

@@

Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.  Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest. We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}). We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix). Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our mathematical observations. 
%The Appendix contains a proof of Lem.~\ref{MainLemma}.

@@

Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$. Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
\begin{align*}
\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
%\leq \varepsilon \sum_{i=1}^k |c_i| \\
\leq \varepsilon \|\mathbf{c}\|_1
\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality follows directly from \eqref{Ldef}. From Def.~\ref{dDef}:
\begin{align}\label{rhs222}
d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
\leq \varepsilon \frac{C_1}{C_2}.
\end{align}
%
Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
\end{proof}

>>>>

%\title{When can a generating dictionary and sparse codes be recovered from noisy data?}
%\title{When is the dictionary learning problem well-posed?}
\title{On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals}
%\title{When is the dictionary learning problem for sparse coding well-posed?}
%\title{When is the sparsest representation unique?}
%\title{When are sparse codes identifiable from their unknown noisy compressive measurements?}
% FRITZ2: The title doesn't reflect the amount of new stuff, it seems incremental from the last one. It's not very meaningful.
% FRITZ: Not everyone knows what well-posed means. You should mention recovery from noisy data in the title.

@@

Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.  Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest. We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}). We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix). Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open problems. 
%The Appendix contains a proof of Lem.~\ref{MainLemma}.

@@

Fixing $\mathbf{y} \in \bm{\mathcal{A}}_S \setminus \{\mathbf{0}\}$, there then exists $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k \setminus \{\mathbf{0}\}$ such that $\mathbf{y} = \mathbf{AX}_K\mathbf{c}$. Setting \mbox{$\mathbf{\overline{y}} = \mathbf{B\overline{X}}_K\mathbf{c}$, which is in $\bm{\mathcal{B}}_{\overline S}$}, we have by triangle inequality:
\begin{align*}
\|\mathbf{y} - \mathbf{\overline{y}}\|_2 
%&= \|\sum_{i=1}^k c_i(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)_i\|_2
&= \|(\mathbf{AX}_K - \mathbf{B\overline{X}}_K)\mathbf{c}\|_2
%\leq \varepsilon \sum_{i=1}^k |c_i| \\
\leq \varepsilon \|\mathbf{c}\|_1
\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2  \\
&\leq \frac{\varepsilon}{L_k(\mathbf{AX}_K)} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality uses \eqref{Ldef}. From Def.~\ref{dDef}:
\begin{align}\label{rhs222}
d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\overline S}) 
\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{K}) } 
\leq \frac{\varepsilon}{  L_k(\mathbf{AX}_{I(S)}) } 
\leq \varepsilon \frac{C_1}{C_2}.
\end{align}
%
Finally, apply Lem.~\ref{MainLemma} with $\varepsilon < L_2(\mathbf{A})/C_1$ and $\pi(S) := \overline S$. % L_2(A) > 0 by def of L, since L_2H(A) > 0 and H covers [m]
\end{proof}
